Normalized Coherence

### 2020-03-11 Analysis/03_Normalized_Coherence.Rmd
add code for msig slopes (still running)

```{r}
# Reading in Biogrid data
biogrid = read_tsv("./data/BIOGRID-ALL-3.5.174.mitab.txt.gz")
biogrid = biogrid %>% filter(`Taxid Interactor A` == "taxid:9606" & `Taxid Interactor B` == "taxid:9606")

@@

@@

>>>>

```{r}
# Reading in Biogrid data
biogrid = read_tsv("./data/BIOGRID-ALL-3.5.174.mitab.txt")
biogrid = biogrid %>% filter(`Taxid Interactor A` == "taxid:9606" & `Taxid Interactor B` == "taxid:9606")

@@

get_msig_ci = function(sub_cats, database) {
  require(msigdbr)
  msig = msigdbr()

  #Getting slopes from each diseases
  mod_over = mod_over %>% group_by(Disease, Category, Num_Genes) %>%
    do({
      mod = lm(sqrt(External) ~ sqrt(Internal)-1, data = .)
      data.frame(Lower = confint(mod)[1], Upper = confint(mod)[2])
    }) 
  #Rename x (Default do tidy result) to Slope
  return(mod_over)
}
```

@@

# Getting 95% between internal/external edges from GOCC, KEGG and REACTOME pathways

```{r}
# Getting biogrid msig slopes
msig_frame_biogrid_ci = get_msig_ci(sub_cats = subcats, database = biogrid)

# Getting string msig slopes
msig_frame_string_ci = get_msig_ci(sub_cats = subcats, database = string)

# Getting string filtered msig slopes
msig_frame_string_filt_ci = get_msig_ci(sub_cats = subcats, database = string_filt)

# Saving the files
saveRDS(msig_frame_biogrid_ci, "Biogrid_Msig_CI.rds")
saveRDS(msig_frame_string_ci, "String_Msig_CI.rds")
saveRDS(msig_frame_string_filt_ci, "String_Filt_Msig_CI.rds")
```
